IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-07-07 paper/appendix.tex
minor
a_l is not in surface syntax

Here we formally define the syntax and semantics of the extensions
sketched in Section~\ref{sec:extensions}.
In Figure~\ref{fig:labeled-vals} we show how labeled values can be added,
while Figure~\ref{fig:labeled-refs} details labeled references formally.
For labeled values, we assume that the constructor |Labeled| is not part
of the surface syntax, but rather an internal construct.
These changes to the semantics require us to update the erasure function
|erasef il|, whose full definition is shown in Figure~\ref{fig:erasure2}.
Note that the soundness proof in Appendix~\ref{sec:appendix}
is done for the fully extended language with labeled values and
labeled references.

\begin{figure}
  %{
  %format .->  = "\overset{\alpha}{\hookrightarrow}"
  %format .-/>  = "\not\overset{\alpha}{\hookrightarrow}"
  \begin{code}
    iv  ::= cdots | Labeled il ie
    ie  ::= cdots | label ie ie | unlabel ie | labelOf ie
    iE  ::= cdots | label iE ie | unlabel iE | labelOf iE
  \end{code}
  \begin{mathpar}
    \inferrule[I-label]
    {|
      il canFlowTo il'
    |}
    {|
      niconf iS id il (label il' ie)
      ->
      niconf iS id il (Labeled il' ie)
    |}
    \and
    \inferrule[I-unlabel]
    {|
      il''=il lub il'
    |}
    {|
      niconf iS id il (unlabel (Labeled il' ie))
      ->
      niconf iS id (il'') ie
    |}
    \and
    \inferrule[I-labelOf]
    {|
    |}
    {|
      niconf iS id il (labelOf (Labeled il' ie))
      ->
      niconf iS id il (il')
    |}
  \end{mathpar}
  \caption{Syntax and semantics for labeled values.  These rules are
    understood to be an addition to the existing rules given earlier.}
  \label{fig:labeled-vals}
  %}
\end{figure}

>>>>

Here we formally define the syntax and semantics of the extensions
sketched in Section~\ref{sec:extensions}.
In Figure~\ref{fig:labeled-vals} we show how labeled values can be added,
while Figure~\ref{fig:labeled-refs} details labeled references formally.
For labeled values, we assume that the constructor |Labeled| is not part
of the surface syntax, but rather an internal construct.  Similarly,
the construct |ial| is internal in the labeled reference implementation.
These changes to the semantics require us to update the erasure function
|erasef il|, whose full definition is shown in Figure~\ref{fig:erasure2}.
Note that the soundness proof in Appendix~\ref{sec:appendix}
is done for the fully extended language with labeled values and
labeled references.

\begin{figure}
  %{
  %format .->  = "\overset{\alpha}{\hookrightarrow}"
  %format .-/>  = "\not\overset{\alpha}{\hookrightarrow}"
  \begin{code}
    iv  ::= cdots | Labeled il ie
    ie  ::= cdots | label ie ie | unlabel ie | labelOf ie
    iE  ::= cdots | label iE ie | unlabel iE | labelOf iE
  \end{code}
  \begin{mathpar}
    \inferrule[I-label]
    {|
      il canFlowTo il'
    |}
    {|
      niconf iS id il (label il' ie)
      ->
      niconf iS id il (Labeled il' ie)
    |}
    \and
    \inferrule[I-unlabel]
    {}
    {|
      niconf iS id il (unlabel (Labeled il' ie))
      ->
      niconf iS id (il  lub il' ) ie
    |}
    \and
    \inferrule[I-labelOf]
    {|
    |}
    {|
      niconf iS id il (labelOf (Labeled il' ie))
      ->
      niconf iS id il (il')
    |}
  \end{mathpar}
  \caption{Syntax and semantics for labeled values.  These rules are
    understood to be an addition to the existing rules given earlier.}
  \label{fig:labeled-vals}
  %}
\end{figure}
